paper_figs_rotations202010 : create paper figures from rotation runs

### 2020-12-14 inst/documents/paper_figs_rotations202010.Rmd
figure tweaks

---
title: "paper_figs_rotations201911 : create paper figures from rotation runs"
#output: pdf_document
output: word_document
author: "Andy South, Sam Jones and Ian Hastings"
date: "`r Sys.Date()`"
---

@@

```{r, eval=TRUE, include=FALSE}
#set to eval=TRUE to make figs for submission

@@

# options to create final publication quality figures
# word doc summarises & figs get stored
opts_chunk$set(dev="tiff",
               dev.args=list(compression="lzw"),
               dpi=300,
               cache=FALSE,
               fig.path='rotfigs/',
               fig.width=8.5,
               fig.height=8.5)
```

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
  library(rotations)
  library(ggplot2)
  library(gridExtra)
  library(tidyverse)
  library(patchwork) #for arranging multiple plots on page

@@

```{r fig2-examp-run-A1, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

# TODO put into a reusable function to plot seq vs rot
# TODO probably allow run_rot to return the ggplot object

@@

```{r fig3-examp-run-A2, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

#TODO replace later, quick pasted test to see effect of adding cost

@@

```{r fig4-examp-run-C2, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

@@

@@

ggseq <- rot_plot_resistance(dfseq, plot=FALSE, plot_mort=TRUE, plot_refuge = FALSE, logy =FALSE  )
ggrot <- rot_plot_resistance(dfrot, plot=FALSE, plot_mort=TRUE, plot_refuge = FALSE, logy =FALSE  )

@@

```{r fig5-examp-run-A3, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

#TODO replace later, quick pasted test to see effect of adding dispersal

@@

```{r fig6-examp-run-B2, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

@@

# calc percentage difference between rotation and sequence
df_res_16$rms_percent <- 100 * df_res_16$gens_rot_minus_seq / df_res_16$gens_seq

@@

```{r figx1-pcent-diff-rot-seq, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

@@

```{r figx2-which-best-each-gens-rot, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

#oooo this is interesting
#it shows what gens_rot the best strategies occur at
ggplot(df_res_16, aes(x=gens_rot, fill=best_strategy)) + 
     geom_histogram(binwidth=widthbin, colour='darkgrey') + 
     scale_fill_manual(values=colrs) +
     theme_minimal() +
     #xlim(-100,100) +
     xlab("generations to reach thresholds for ROTATION") +
     ylab("count of randomly sampled runs") +    
     theme(panel.grid.minor=element_blank(),
           legend.position="bottom") +
     facet_grid(rows=vars(id14), cols=vars(idAD),
                labeller=labeller(idAD=idAD_lookup, id14=id14_lookup))

@@

```{r figx3-which-best-each-gens-seq, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

#gens_seq the best strategies occur at
ggplot(df_res_16, aes(x=gens_seq, fill=best_strategy)) + 
     geom_histogram(binwidth=widthbin, colour='darkgrey') + 
     scale_fill_manual(values=colrs) +
     theme_minimal() +
     #xlim(-100,100) +
     xlab("generations to reach thresholds for SEQUENCE") +
     ylab("count of randomly sampled runs") +    
     theme(panel.grid.minor=element_blank(),
           legend.position="bottom") +
     facet_grid(rows=vars(id14), cols=vars(idAD),
                labeller=labeller(idAD=idAD_lookup, id14=id14_lookup))

@@

\pagebreak

@@

```{r, eval=FALSE, echo=FALSE, warning=FALSE, message=FALSE, fig.width=9, fig.height=5}

# doesn't show much
# Plots of how the difference between rotations and sequences respond to model inputs.

# go through selected inputs and plot them on x with gens_rot_minus_seq on y 
# TODO check whether this covers all the inputs we want to look at
in_cols <- c('cost','dom_cos','dom_sel','rr','expo_hi','male_expo_prop','eff','start_freqs')

y <- 'gens_rot_minus_seq'

for(i in in_cols)
{

    #plotnum <- plotnum + 1

    #print( ggplot(ggInsOuts, aes_string(x=i, y=y, colour="strategy")) + 
    #plotlist[[plotnum]] <- 
    print( ggplot(df_res_16, aes_string(x=i, y=y)) +

             geom_point(shape=1, size=1, alpha=0.5, show.legend=FALSE) +
             theme_minimal() +
             geom_smooth(linetype='dashed',size=0.5) )

# PRCC to show the sensitivity of the difference between rotation and sequence to inputs
# this can only be used for the experiments where all insecticides are the same
# (because in the ones where insecticides differ there are multiple values for each input)
# start by running on just A expts

```{r figxx-PRCC, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

  library(sensitivity)

# pcc(X, y, rank = FALSE, nboot = 0, conf = 0.95)
# 
# Arguments
# X a data frame containing model input variables
# y a vector containing the responses 
# rank logical. If TRUE, the analysis is done on the ranks.
# nboot the number of bootstrap replicates.
# conf the confidence level of the bootstrap confidence intervals.

#same as above
#TODO check that this covers all the inputs we want to look at
in_cols <- c('cost','dom_cos','dom_sel','rr','expo_hi','male_expo_prop','eff','start_freqs')

    x <- df_res_A[,in_cols]
    y <- df_res_A['gens_rot_minus_seq']

    pcc_res <- pcc(x, y, rank=TRUE)

    #if you add bootstrap, error bars are added to the default plot & extra columns to the PRCC object
    #pcc_res <- pcc(x, y, rank=TRUE, nboot=100)
    #plot(pcc_res)

    #results are here I can probably rbind them together into a df that I can ggplot
    #pcc_res$PRCC

    to_plot <- pcc_res$PRCC
    #rename column 1 from 'original to PRCC
    names(to_plot)[1] <- 'PRCC'
    to_plot$inputs <- rownames(to_plot)

    axis_text_x <- element_text(angle = 45,hjust = 1, vjust = 1)
    height <- 0.9

    gg <- ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) +     
             geom_point(shape=1, colour='red') +
             theme(axis.text.x = axis_text_x) +
             geom_hline(yintercept = 0, linetype=3) +
             #theme(panel.grid.major.y = element_line(color = "grey", size = 1)) +
             ylim(-1,1) +
             #ggtitle(paste(strat_name[strategy_num])) +
             ggtitle("Effect of inputs on benefit of rotations, all A expts.") +
             xlab(NULL)

    plot(gg)

  #to put back in some ref gridlines that are removed by cowplot
  #theme_set(theme_gray())
  #theme_set(theme_bw())

  #plot_grid( plotlist[[1]],plotlist[[2]],plotlist[[3]],plotlist[[4]],ncol=1, rel_heights=c(1,1,1,1.8))  
  #plot_grid( plotlist[[1]],plotlist[[2]],plotlist[[3]],ncol=1, rel_heights=c(1,1,1.6), labels='AUTO')

```{r, eval=FALSE, echo=FALSE, warning=FALSE, message=FALSE, fig.width=9, fig.height=5}

# Runs where rotations are >20% better (in red) are associated with higher dominance of cost and lower dominance of selection, but doesn't guarantee, must be interaction with other inputs too.
# this was for earlier runs when there was some strange model behaviour, may not be the case now
# and may not be very meaningful anyway

#'cost','dom_cos','dom_sel','rr','expo_hi','male_expo_prop','eff','start_freqs'

#'cost','dom_cos','dom_sel'

y <- 'gens_rot_minus_seq'

ggplot(df_res_16, aes(x=dom_sel, y=dom_cos)) + 
     geom_point(shape=3, size=1, alpha=0.2, show.legend=FALSE) +
     theme_minimal() +
     geom_point(data=filter(df_res_16, gens_rot_minus_seq/gens_seq >= 0.3 ), shape=1, size=1, col='red', alpha=0.8)

```{r, eval=FALSE, echo=FALSE, warning=FALSE, message=FALSE, fig.width=9, fig.height=6}
#eval=FALSE tmp because changes above will break this
# summary plot of all runs, would show any differences between sequence & rotations as non horizontal lines

# want to plot line between sequence and rotation value
# any deviation from horizontal will be obvious
# could use rotation interval as the x axis, so that longer intervals will be clearer

# maybe not for publication
# but useful for quick view

#it was useful for me but now that I've moved to one row per scenario it won't work !!

    gg <- ggplot( df_res_16, aes_string(x='rot_interval',
                                         y='tot_gens_dep_under50',
                                         group='scenario',
                                         colour='scenario') ) +
          geom_line( alpha=0.5, lwd=1 )

    plot(gg)

# plot gens againts exposure and effectiveness
# as a quick test to see if I can set the starting values of these higher

    gg <- ggplot( df_res_16, aes_string(x='eff',
                                         y='tot_gens_dep_under50') ) +
          geom_point( alpha=0.5 )
    plot(gg)

    gg <- ggplot( df_res_16, aes_string(x='expo_hi',
                                         y='tot_gens_dep_under50') ) +
          geom_point( alpha=0.5 )
    plot(gg)

    gg <- ggplot( df_res_16, aes_string(x='expo_hi*eff*male_expo_prop',
                                         y='tot_gens_dep_under50') ) +
          geom_point( alpha=0.5 )
    plot(gg)

# new - mean mortality over whole sim
# slightly surprising that not much variation
# this one colours by best strategy in generation terms
# B1 suggests that runs where rotation is better may have
# lower mortality under rotation
# try to find a different way of showing that 
# (e.g. just plot gens_diff against mortality diff)

```{r figxmort-rot, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

# ** mean mortality for rotations

# have a go at classifying gens_rot so I can use it to colour the mean mort bars
# cut(gens_rot, 5) this does that

ggplot(df_res_16, aes(x=mort_rot, fill = cut(gens_rot, 5))) + 
#ggplot(df_res_16, aes(x=mort_rot_minus_seq)) +   
     geom_histogram(colour='darkgrey') + 
     #geom_histogram(binwidth=0.02, colour='darkgrey') + 
     #be interesting to color by generations to see if strategies that last longer have lower mortality ?
     #scale_fill_manual(values=colrs) +
     #scale_fill_continuous(aes(gens_rot)) +
     scale_fill_brewer(palette = 'greens') +
     theme_minimal() +
     #xlim(-100,100) +
     xlab("mean mortality over all generations for rotation") +
     ylab("count of randomly sampled runs") +  
     theme(panel.grid.minor=element_blank(),
           legend.position="bottom") +
     facet_grid(rows=vars(id14), cols=vars(idAD),
                labeller=labeller(idAD=idAD_lookup, id14=id14_lookup))

```{r figxgens_rot_v_mort_rot, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

# ** mean mortality for rotations

ggplot(df_res_16, aes(x=gens_rot, fill = cut(mort_rot, 5))) + 
#ggplot(df_res_16, aes(x=mort_rot_minus_seq)) +   
     geom_histogram(colour='darkgrey') + 
     #geom_histogram(binwidth=0.02, colour='darkgrey') + 
     #be interesting to color by generations to see if strategies that last longer have lower mortality ?
     #scale_fill_manual(values=colrs) +
     #scale_fill_continuous(aes(gens_rot)) +
     scale_fill_brewer(palette = 'greens') +
     theme_minimal() +
     #xlim(-100,100) +
     #xlab("mean mortality over all generations for rotation") +
     #ylab("count of randomly sampled runs") +  
     theme(panel.grid.minor=element_blank(),
           legend.position="bottom") +
     facet_grid(rows=vars(id14), cols=vars(idAD),
                labeller=labeller(idAD=idAD_lookup, id14=id14_lookup))

```{r figxmort_rot_v_start_freqs, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

# i expect that mean mort may be largely influenced by startfreqs, but remember when diff. there are multiple

# ** mean mortality for rotations

ggplot(df_res_16, aes(x=start_freqs, y=mort_rot)) + 
#ggplot(df_res_16, aes(x=mort_rot_minus_seq)) +   
     #geom_histogram(binwidth=widthbin, colour='darkgrey') + 
     geom_hline(yintercept = 0, linetype="dashed", color = 'darkgrey') +
     geom_vline(xintercept = 0, linetype="dashed", color = 'darkgrey') +
     geom_point(shape='.') +
     geom_smooth() +
     #geom_abline() +
     # scale_fill_manual(values=colrs) +
     theme_minimal() +
     # #xlim(-100,100) +
     # xlab("advantage of rotations over sequence in mean mortality") +
     # ylab("count of randomly sampled runs") +  
     theme(panel.grid.minor=element_blank()) +
     facet_grid(rows=vars(id14), cols=vars(idAD),
                labeller=labeller(idAD=idAD_lookup, id14=id14_lookup))

```{r figxmort-rot-minus-seq, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

# ** mean mortality difference between rot & seq
# why do these seem not to sum to totals ?

#ggplot(df_res_16, aes(x=mort_rot_minus_seq, fill=best_strategy)) + 
ggplot(df_res_16, aes(x=mort_rot_minus_seq)) +   
     geom_histogram(binwidth=0.02, colour='darkgrey') + 
     #scale_fill_manual(values=colrs) +
     theme_minimal() +
     #xlim(-100,100) +
     xlab("advantage of rotations over sequence in mean mortality") +
     ylab("count of randomly sampled runs") +  
     theme(panel.grid.minor=element_blank(),
           legend.position="bottom") +
     facet_grid(rows=vars(id14), cols=vars(idAD),
                labeller=labeller(idAD=idAD_lookup, id14=id14_lookup))

```{r figxmort-which-best-meanmort, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

ggplot(df_res_16, aes(x=mort_rot_minus_seq, fill=best_strategy)) + 
#ggplot(df_res_16, aes(x=mort_rot_minus_seq)) +   
     #geom_histogram(binwidth=widthbin, colour='darkgrey') + 
     geom_histogram(binwidth=0.02, colour='darkgrey') + 
     scale_fill_manual(values=colrs) +
     theme_minimal() +
     xlim(-0.2,0.2) +
     xlab("advantage of rotations over sequence in mean mortality") +
     ylab("count of randomly sampled runs") +  
     theme(panel.grid.minor=element_blank(),
           legend.position="bottom") +
     facet_grid(rows=vars(id14), cols=vars(idAD),
                labeller=labeller(idAD=idAD_lookup, id14=id14_lookup))

#try to establish whether
#runs that have higher generations for rotations
#also have lower mean mortality

```{r figxmort-v-gens, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

#gens_rot_minus_seq, facet by A-D and 1-4, better facet labels
ggplot(df_res_16, aes(x=gens_rot_minus_seq, y=mort_rot_minus_seq)) + 
#ggplot(df_res_16, aes(x=mort_rot_minus_seq)) +   
     #geom_histogram(binwidth=widthbin, colour='darkgrey') + 
     geom_hline(yintercept = 0, linetype="dashed", color = 'darkgrey') +
     geom_vline(xintercept = 0, linetype="dashed", color = 'darkgrey') +
     geom_point(shape='.') +
     geom_smooth(method='lm') +
     #geom_abline() +
     # scale_fill_manual(values=colrs) +
     theme_minimal() +
     # #xlim(-100,100) +
     # xlab("advantage of rotations over sequence in mean mortality") +
     # ylab("count of randomly sampled runs") +  
     theme(panel.grid.minor=element_blank()) +
     facet_grid(rows=vars(id14), cols=vars(idAD),
                labeller=labeller(idAD=idAD_lookup, id14=id14_lookup))

>>>>

---
title: "paper_figs_rotations202010 : create paper figures from rotation runs"
#output: pdf_document
output: word_document
author: "Andy South, Sam Jones and Ian Hastings"
date: "`r Sys.Date()`"
---

@@

```{r setup, eval=TRUE, include=FALSE}
#set to eval=TRUE to make figs for submission

@@

# options to create final publication quality figures
# word doc summarises & figs get stored
opts_chunk$set(dev="tiff",
               dev.args=list(compression="lzw"),
               dpi=300,
               cache=FALSE,
               fig.path='rotfigs/',
               fig.width=8.5,
               fig.height=8.5)

  library(rotations)
  library(ggplot2)
  library(gridExtra)
  library(tidyverse)
  library(patchwork) #for arranging multiple plots on page

@@

```{r fig4-examp-run-A1, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

#2020-10 was fig2

@@

```{r fig5-examp-run-A2, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

#2020-10 was fig3

@@

```{r fig6-examp-run-C2, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

@@

#2020-10 was fig4

@@

ggseq <- rot_plot_resistance(dfseq, plot=FALSE, plot_mort=TRUE, plot_refuge = FALSE, logy =FALSE, legend_title = '' )
ggrot <- rot_plot_resistance(dfrot, plot=FALSE, plot_mort=TRUE, plot_refuge = FALSE, logy =FALSE  )

@@

```{r fig7-examp-run-A3, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

#2020-10 was fig5

@@

```{r fig8-examp-run-B2, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

#2020-10 was fig6

@@

# calc percentage difference between rotation and sequence for resistance & mortality
df_res_16$rms_percent <- 100 * df_res_16$gens_rot_minus_seq / df_res_16$gens_seq
df_res_16$rms_mort_percent <- 100 * df_res_16$mort_rot_minus_seq / df_res_16$mort_seq
#seems problem with above try Ians way
df_res_16$rms_mort_percent <- 100 * (df_res_16$mort_rot / df_res_16$mort_seq -1)
# Ian said this is equivalent and it does give nearly same result 10pow-14 difference
#df_res_16$ian_rms_percent <- 100 * (df_res_16$gens_rot / df_res_16$gens_seq -1)
#df_res_16$tst <- df_res_16$ian_rms_percent-df_res_16$rms_percent

@@

```{r fig2-pcent-diff-rot-seq, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

# 2020-10 previously fig7

@@

```{r fig3-mort-which-best-meanmort, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

# 2020-10 previously fig8

#2020-10-08 Ian asked to change this to percent difference

ggplot(df_res_16, aes(x=rms_mort_percent, fill=best_strategy)) + 
#ggplot(df_res_16, aes(x=mort_rot_minus_seq, fill=best_strategy)) + 
#ggplot(df_res_16, aes(x=mort_rot_minus_seq)) +   
     #geom_histogram(binwidth=widthbin, colour='darkgrey') + 
     geom_histogram(binwidth=5, colour='darkgrey') + 
     scale_fill_manual(values=colrs) +
     theme_minimal() +
     xlim(-40,40) +
     xlab("percentage advantage of rotations over sequence in mean mortality") +  
     ylab("count of randomly sampled runs") +  
     theme(panel.grid.minor=element_blank(),
           legend.position="bottom") +
     facet_grid(rows=vars(id14), cols=vars(idAD),
                labeller=labeller(idAD=idAD_lookup, id14=id14_lookup))

#old version just mortality rather than %
# ggplot(df_res_16, aes(x=mort_rot_minus_seq, fill=best_strategy)) + 
#      geom_histogram(binwidth=0.02, colour='darkgrey') + 
#      scale_fill_manual(values=colrs) +
#      theme_minimal() +
#      xlim(-0.2,0.2) +
#      xlab("advantage of rotations over sequence in mean mortality") +
#      ylab("count of randomly sampled runs") +  
#      theme(panel.grid.minor=element_blank(),
#            legend.position="bottom") +
#      facet_grid(rows=vars(id14), cols=vars(idAD),
#                 labeller=labeller(idAD=idAD_lookup, id14=id14_lookup))

@@

```{r fig9-which-best-each-gens-rot, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

# 2020-10 fig9

#oooo this is interesting
#it shows what gens_rot the best strategies occur at

# but difficult to see the ones where there is an advantage to either strategy because so few of them 
# increasing binwidth to 50 made advantage run more visible

#also good that it shows runs lasting longer when fitness costs and dispersal are added

ggplot(df_res_16, aes(x=gens_rot, fill=best_strategy)) + 
     geom_histogram(binwidth=50, colour='darkgrey') + 
     scale_fill_manual(values=colrs) +
     theme_minimal() +
     #scale_y_log10() + #log scale did make it easier to see lower values but misleading
     #xlim(-100,100) +
     xlab("generations to reach thresholds for ROTATION") +
     ylab("count of randomly sampled runs") +    
     theme(panel.grid.minor=element_blank(),
           legend.position="bottom") +
     facet_grid(rows=vars(id14), cols=vars(idAD),
                labeller=labeller(idAD=idAD_lookup, id14=id14_lookup))

#Ian asked if could make the bars mean of rot & seq
#but I think this is confusing & potentially wrong
# ggplot(df_res_16, aes(x=0.5*(gens_rot+gens_seq), fill=best_strategy)) + 
#      geom_histogram(binwidth=50, colour='darkgrey') + 
#      scale_fill_manual(values=colrs) +
#      theme_minimal() +
#      #scale_y_log10() + #log scale did make it easier to see lower values but misleading
#      #xlim(-100,100) +
#      xlab("generations to reach thresholds for ROTATION") +
#      ylab("count of randomly sampled runs") +    
#      theme(panel.grid.minor=element_blank(),
#            legend.position="bottom") +
#      facet_grid(rows=vars(id14), cols=vars(idAD),
#                 labeller=labeller(idAD=idAD_lookup, id14=id14_lookup))

@@

```{r fig9seq-which-best-each-gens-seq, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

#same as previous but for seq rather than rot
#maybe to go in SI

#gens_seq the best strategies occur at
ggplot(df_res_16, aes(x=gens_seq, fill=best_strategy)) + 
     geom_histogram(binwidth=50, colour='darkgrey') + 
     scale_fill_manual(values=colrs) +
     theme_minimal() +
     #xlim(-100,100) +
     xlab("generations to reach thresholds for SEQUENCE") +
     ylab("count of randomly sampled runs") +    
     theme(panel.grid.minor=element_blank(),
           legend.position="bottom") +
     facet_grid(rows=vars(id14), cols=vars(idAD),
                labeller=labeller(idAD=idAD_lookup, id14=id14_lookup))

@@

### 2020-12-14 inst/documents/rotations_notes.Rmd
figure tweaks

# TODO

2020-02-25 : probably get Sam to rerun the 16k runs

first try to fix the issues above, or check they don't cause problems

@@

Try some rotation_runs2019.Rmd with new outputs.

a. create a function to compare seq and rot plots
1. check random number issues
2. look at paper3 folder

Questions to answer re 16k runs :

1. why with mortality switch are there more runs favouring sequence ?

check on dispersal limits using new method. Seems that anything above 0.4 leads to near complete mixing
run_rot(migration=0.4, coverage=0.5)
#interesting how small levels of migration cause resistance freqs to decline even with no costs

write word description of what dispersal does
rename migration to dispersal ?

migration limits ???
I need to check on them more ! to make sure I know what they are doing.

@@

~ create some plot functions to work on the output files (df_res_all) e.g. plot_rotseq_diff()

~ try to get run progress message into console or terminal
~ improve readme.md with details of how to run simulations

@@

~ TIDY UP CODE AND IMPROVE DOCUMENTATION e.g. function args

whatever I do I need to make mort/survival thing more transparent

options
~ pass as mortality and then convert to survival for calculation
~ pass as survival convert to mortality for plot

~ ian interested in starting frequencies at 10e-4, can do that for the runs with different values per insecticide.
~ we won't run sensitivity analysis on those runs, but just to check that rotations and sequence runs still similar

rotations paper :
~ think about what questions managers will want answered

A) when do both strategies work (include looking at insecticides and rotation level)
 - maybe do PRCC
B) if neither work, when are rotations better ?

small changes :
~ dominance of resistance
~ how to term success. 'At least one insecticide still below resistance thresholds'

Look into whether to use min_rwr_interval OR min_gens_switch_back 
I'm thinking that I'll stick with min_rwr_interval

I think takehome message maybe that rotations are much better than sequences only in rare circumstances.

May also be something useful I can say about the number of insecticides too ? (Which is of interest to IVCC).

~ can I create some simple figs to illustrate how an increasing rate of resistance evolution with frequency can lead to rotations being favoured

~ modify sensi_an_rotations so that I have a reproduceable record of a) no cost or dispersal b)cost only c)dispersal only, d) cost & dispersal

think about killer plot to display difference between rot & seq generations

~ maybe come back to i_in_use ribbons not meeting issue
~ add in some unit-tests ?

~ can we do cross resistance within the rotations model ? i.e. that resistance to one insecticide also provides some protection against another ? I don't think so because it requires linkage.

~ add error-check to run_rot if n.insecticides=1 & migration > 0

Maybe explore idea from Rowland (1981) that resistance declines faster when it is mostly held by the RR (i.e. at higher allele frequencies)

Look into data on changing allele frequencies over time (e.g. for Kdr)...

It occurred to me that maybe a benefit of rotations is that if it is difficult to measure resistance allele frequencies they provide a lower risk of reaching resistance thresholds for any insecticide. i.e. are they a better strategy in light of uncertainty in resistance allele frequencies ?

~ can we get cost to decrease over time at high frequency as suggested in GPIRM ?

BEWARE active in active_or_refuge is potentially confusing, does not mean that insecticide is active/deployed, just means its is the active area (a different insecticide may be deployed)

@@

~ Ian & I talked about using fitness to determine changes. and that fitness could be used as an index of population, but Ian was sceptical, he said to look up fitness determinants of population on wikipedia, about soft & hard selection.

~ test fitness_single_locus() from run_rot() and add to Rmd

@@

# state of play
~ sensi_an_rotations1.Rmd : starting on sensitivity analysis
~~  produces an output dataframe containing both inputs and outputs
~~ saves outputs to df_res_all_rot.rda

>>>>

2020-02-25 : get Sam to rerun the 16k runs

#2020-10-05 reviewing runs for rotations paper & Qs from Ian

Andy….I assume the following description is how you transformed the data to plot Figure 7 ?
We quantify the relative performance of sequential and rotations policy (see later discussion of Figures 7 and 8) using the metric, z.
z=(L(r)/L(s) -1)*100

this is my fig x1, the output is rms_percent

df_res_16$rms_percent <- 100 * df_res_16$gens_rot_minus_seq / df_res_16$gens_seq

Ian asks to change the mortality fig (8) to %difference.

I think it is :
figxmort-which-best-meanmort

The rational for keeping it to absolute mortality differences is that the values are meaningful to those interested in insecticide resistance, and that mortality is already a %, so talking about percent of a percent gets really confusing.
Currently the figure shows that most runs result in just a 1% difference in mortality - that readers may equate e.g. to the difference between 89 & 90% in a bioassay.

# TODO 2020-20

# TODO (from before)

@@

check on dispersal limits using new method. Seems that anything above 0.4 leads to near complete mixing
run_rot(migration=0.4, coverage=0.5)
interesting how small levels of migration cause resistance freqs to decline even with no costs
write word description of what dispersal does
rename migration to dispersal ?
migration limits ??? I need to check on them more ! to make sure I know what they are doing.

@@

@@

@@

@@

# state of play
~ sensi_an_rotations1.Rmd
~~  produces an output dataframe containing both inputs and outputs
~~ saves outputs to df_res_all_rot.rda
